BOLD Parameter Estimation Using Particle Filters

### 2010-08-15 doc/thesis/methods.tex
removed the todo items

Typically a step size of .001 was used, after finding that even .01 can
at times lead to the state equations careening out of control.

@@

TODO give scanner details

@@

\subsection{Runtime}
The run-time for a single voxel depends on the several factors. First, the
overall length of the signal being analyzed. For 1000 measurements it takes
about 6 minutes. On the other hand, in real circumstances the
length is only around 150 measurements and takes around 40 seconds (for 1000 
particles, 1500 integration points and a Quad Core CPU). The size of 
local linearization steps are also crucial although going above .001 seconds
per step is not recommended. In most cases millisecond resolution
is fine; however, when generating simulated data I found that at times it was
still not enough every once. This is problematic in the actual particle
filter since, given the large number of simultaneous integrations taking 
place, its probable that a few particles will fail and be unfairly thrown away.
To prevent such events, 1500 integration points per second were used throughout
the tests.

>>>>

For all the analyses  in this work, $1400$ integration points
per second were used.  Typically a step size of $0.001$ was sufficient,
however, from time to time $0.001$ can still be too high for the
BOLD model.

@@

The resting state was gathered in the exact same way as the data in 
\autoref{sec:ExperimentConfig}, except without the stimuli.

@@

\subsection{Runtime}
The run-time for a single voxel depends on the several factors. First, the
overall length of the signal being analyzed. For 1000 measurements it takes
about 6 minutes. On the other hand, in real circumstances the
length is only around 150 measurements and takes around 40 seconds (for 1000 
particles, 1500 integration points and a Quad Core CPU). The size of 
local linearization steps are also crucial although going above $0.001$ seconds
per step is not recommended. In most cases millisecond resolution
is fine; however, when generating simulated data I found that at times it was
still not enough every once. This is problematic in the actual particle
filter since, given the large number of simultaneous integrations taking 
place, its probable that a few particles will fail and be unfairly thrown away.
To prevent such events, 1500 integration points per second were used throughout
the tests.
